### 2012-02-16 docs/notes.tex
Edit notes.

Statistical methods for analyzing network data have become increasingly useful for studying  phenomenon ranging from people communicating online to protein interactions \cite{Goldenberg2009}. One class of statistical models for network data uses latent variables for each node to help capture unobserved heterogeneity.  For example, the stochastic blockmodel \cite{Nowicki2001, Kemp} assumes each node in the network belongs to some block (or cluster) and parametrizes the probability of edges between blocks.   Such approaches are especially useful for large-scale network data where higher-order dependencies can cause models such as exponential random graph models to be too complex to fit.

Network data, however, is often collected as a sequence of events occurring over time.   Recently several works have adapted models from survival analysis and event history analysis to provide continuous time models of network-based event data \cite{Butts2008,Brandes2009,Perry2011,Stadtfeld2010,Stadtfeld2011,Opsahl2011,Vu2011,Vu2011a}.  These models allow one to specify the dependence of the process on the previous history of events.  In this way one may incorporate theories about the underlying processes and make predictions about future data conditioned on the past.

The above continuous time network models have two major drawbacks: 1) the entire network is assumed to have identical dynamics, and 2) the occurrence of any event can affect the rate at which any other event occurs.  Both aspects may be unrealistic.  Consider email communication in a small organization comprised of several teams.  Each team may have a different pattern for collaborating via email, and in many cases emails within one team will not affect emailing behavior within a separate team.

Borrowing from the intuition of stochastic blockmodels, we propose a hierarchical model of continuous time network data that learns latent clusters of nodes which share similar patterns of interaction.  [TODO: Explain how our experiments show that this helps.]   [TODO: perhaps use ``role'' terminology.] By combining a latent variable framework with a local dependence model for event sequences, we provide a hierarchical approach for modeling event-based network data, accompanying recent hierarchical extensions for latent position models \cite{Handcock2007} and exponential random graph models \cite{Schweinberger2011}.

@@

%Each interaction then has a set of periods $d \in D_{ij}$ each with a start time $a_d$, an end time $b_d$, and a rate $\lambda_d$.
Consider a nonhomogeneous Poisson process with  intensity $\lambda(t)$ that is piecewise constant with respect to a set of knots $\tau$.  We can then write the likelihood of $M$ events as
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda(t_m) \exp\left\{ - \int_{0}^{t_M} \lambda(s)ds \right\} \\
&= \prod_{m=1}^M \lambda(t_m|\cdot) \prod_{k=1}^{|\tau|} \exp\left\{ - (\tau_{k} - \tau_{k-1}) \lambda(\tau_k) \right\}
\end{align}
\noindent where the $m$th event occurs at time $t_m$, the intensity function $\lambda(t)$ is right continuous, and each $\tau_k \in [0,t_m]$.
% \begin{align}
% \mathcal{L}(A|\theta) &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}}  \exp\left\{ - \int_{0}^{t_M} \lambda_{i}(\tau | \cdot)d\tau \right\} \\
% &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}} \prod_{v \in D_{i}} \exp\left\{ - (b_v - a_v) \lambda_{i}(b_v | \cdot ) \right\}
% \end{align}

It is straightforward extend this to marked point processes where each event contains additional information.  In the context of relational events occurring among $N$ nodes, for example, we let the \emph{risk set} $\mathcal{R}$ of possible events include all allowed dyads.  Let each dyad $(i,j) \in \mathcal{R}$ have an intensity function $\lambda_{ij}(t|\cdot)$ that is piecewise constant.  As shown in Figure \ref{fig:example}, we assume each intensity function $\lambda_{ij}(t)$ may only change following an event involving either $i$ or $j$.  Let $\tau_{i,j,m}$ be the time that $\lambda_{i,j}$ changed before the $m$th event and let $\mathcal{R}_{i,j}$ be the set of dyads involving either $i$ or $j$.  [TODO: We further assume that all intensity functions change at times $t=0$ and $t=t_M$.  Also, assume the first event is drawn uniformly from the risk set.]
% Letting $ \mathcal{R}_{k_1,k_2}$ be the set of events that can occur from $k_1$ to $k_2$ and  $\boldsymbol{\tau}_{i,j}$ is the set of knots where the respective intensities may change, we may write the likelihood as follows:
% \begin{align}
% \mathcal{L}(\mathcal{A}|\theta) %&= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}} \prod_{k=1}^{|\boldsymbol{\tau}_{ij}|} \exp\{ - (\tau_{i,j,k} - \tau_{i,j,k-1}) \lambda_{ij}(\tau_{i,j,k} | \cdot) \} \\
% &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{k_1=1}^K \prod_{k_2=1}^K \prod_{(i,j) \in \mathcal{R}_{k_1,k_2}} \prod_{r=1}^{|\boldsymbol{\tau}_{i,j}|} \exp\{ - (\tau_{k_1,k_2,r} - \tau_{k_1,k_2,r-1}) \lambda_{ij}(\tau_{i,j,r} | \cdot) \} 
% \end{align}
% \begin{align}
% \mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{r=1}^N \exp\{ - (t_m - \tau_{i,r,m}) \lambda_{ir}(t_m | z_i,z_r)  - (t_m - \tau_{r,j,m}) \lambda_{rj}(t_m | z_r,z_j) \} 
% \end{align}
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}_{i_m,j_m}}\exp\{ - (t_m - \tau_{i,j,m}) \lambda_{ij}(t_m | z_i,z_j) \}
\end{align}

@@

For a given dyad $(i,j)$ and time $t$ we may also have a vector of statistics $\mathbf{s}_{ij}(t|\mathcal{A}_t,\mathbf{z})$ that is a function of the previous event history  $\mathcal{A}_t = \{(t_m,i_m,j_m): t_m \in [0,t)\}$  and the latent cluster assignments $\mathbf{z}$.  Note the statistics $\mathbf{s}_{ij}$ also do not change until an event involving either $i$ or $j$ occurs.  We model the intensity functions via a log linear model
\begin{align}
\log \lambda_{ij}(t | \mathcal{A}_t,\mathbf{z}) = \boldsymbol{\beta}_{z_i,z_j} \mathbf{s}(t,i,j|\mathcal{A}_t,\mathbf{z}).
\end{align}
where for each pair of clusters $(z_i,z_j)$ we have a vector of parameters $\boldsymbol{\beta}_{z_i,z_j}$ that corresponds to the covariate vector $\mathbf{s}_{ij}(t|\cdot)$.  This is reminiscent of the stochastic blockmodel \cite{Nowicki2001,Kemp} which models the probability of a dyad as $p(y_{ij}) =\mbox{logit}^{-1}( \eta_{z_i,z_j})$ where $\eta_{z_i,z_j}$ is essentially a mixing rate between group $z_i$ and group $z_j$.  Here, however, the blockmodel structure facilitates the study of intra-group and inter-group dynamics via a continuous-time network model.

@@

We construct $\mathbf{s}_{ij}$ using a similar set of statistics as used in \cite{Butts2008,Vu2011}. Let $v_{ijm} \in [0,M]$ be the index of the last event where $(i,j)$ occurred (n.b. $t_{v_{ijm}} = \tau_{ijm}$). If $(i,j)$ has never occurred, we set $v_{ijm}=0$.  
\begin{enumerate}
\item Sender out-degree: $s_{1}(t,i,j) = \sum_{m:t_m<t} I(i_m=i)$
\item Sender in-degree: $s_{2}(t,i,j) = \sum_{m:t_m<t} I(j_m=i)$
\item Receiver out-degree: $s_{3}(t,i,j) = \sum_{m:t_m<t} I(i_m=j)$
\item Receiver in-degree: $s_{4}(t,i,j) = \sum_{m:t_m<t} I(j_m=j)$
\item Reciprocity (AB-BA): $s_{5}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-taking (AB-BY): $s_{6}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-usurping (AB-XA): $s_{7}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-usurping (AB-XB): $s_{8}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-continuing (AB-AY): $s_{9}(t,i,j) =  I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Number of shared two-paths: $s_{10}(t,i,j) =   \sum_{m:t_m<t} \sum_{r=1}^NI(i_m=i,j_m=r or i_m=r,j_m=j)$
% \item Shared contacts (since last occurrence): $s_{ij10}(t,i,j) = \sum_{r=1}^N I(i_m=i,j_m=j,i_{v_{ijm}}=i,j_{v_{ijm}}=r)$
% \item Triadic closure (since last occurrence): $s_{ij11}(t,i,j) = \sum_{r=1}^N I(i_m=i,j_m=j,i_{v_{ijm}}=r,j_{v_{ijm}}=j)$
% \item Shared contacts (since last occurrence): $s_{ij12}(t,i,j) = \sum_{r=1}^N I(i_m=i,j_m=j,i_{v_{ijm}}=r,j_{v_{ijm}}=r)$
\end{enumerate}

@@

\subsection{Submodels}

The above framework generalizes several important special cases.  The first is one where events within each block share the rate at which they occur.  This can be implemented by only having an intercept statistic, $s_0(t,i,j) = 1$.  As these intensities do not change under this specification, the likelihood simplifies to 
$$\mathcal{L}(\mathcal{A}|\beta) = \prod_{m=1}^M \lambda_{i_m,j_m} \prod_{(i,j) \in \mathcal{R}} \exp\{-t_M \lambda_{i,j}\}$$
where $ \lambda_{ij} = \exp\{\boldsymbol{\beta}_{z_i,z_j}\}$.  Each block in this model is homogeneous Poisson process where the dyad associated with each event is draw uniformly from the dyads in that block.

Another important model is one where within group interactions are governed via a set of parameters while all between group interactions are governed by a different set.  In this case $\boldsymbol{\beta}_{k1,k2} = \boldsymbol{\gamma}$ for all $k1 \ne k2$.

@@

\subsection{Approximate likelihood methods}

TODO: Discuss how one might sample the likelihood.  Cite Raftery paper.

TODO: Look at performance of this with respect to bias and performance measures.

% This involves recomputing each $\boldsymbol{\tau}$ and possibly each $\mathbf{s}_{ij}$ if it also depends on $\mathbf{z}$.

%TODO: Decide how to handle label switching.  Schweinberger has an interesting approach I hadn't seen before for his hierarchical ERGMS.  Should look into that more closely...

% \subsection*{Bookkeeping considerations}
% %For each dyad, we need to keep track of the set of piecewise constant intervals $d_{ij}$.  For a given set of assignments $z$ we can compute these intervals $(a_v,b_v)$.

% Recall we let intensities change whenever an event occurs involving a fellow cluster member.  Thus the vector $\boldsymbol{\tau}_{ij}$ of changepoints (or knots) is given by
% $$\boldsymbol{\tau}_{ij} = \left\{ t_m: z_{i_m} = z_i \ \mbox{or} \ z_{j_m} = z_j, m=1,\ldots,M\right\}$$
% Any time we update we change node $k$'s cluster assignment from $a$ to $b$, the change point vectors for any nodes in $a$ and $b$ must be updated.  For now we assume we have to recompute  $\boldsymbol{\tau}_{ij}$  entirely.  Similarly, if the covariate vectors $\mathbf{s}_{ij}(t)$ depend on $\mathbf{z}$ then we need to recompute those as well prior to computing the likelihood.%More specifically, for a $D_{ij}$ such that $z_i, z_j \in \{a,b\}$, we must add knots $t_m$ for each.

@@

We check our model fitting procedure using a small synthetic data set involving 10 nodes from 2 clusters where 1) the first cluster has an increased tendency for reciprocity, 2) members of the second cluster have an increased tendency to continue speaking, and 3) interactions between groups are more likely to be repeated.  The specification of $\textbf{s}$ is therefore $s_{ij}(t) = [s_0, s_{ij5}(t), s_{ij9}(t), s_{ij11}(t)]$.  For the synthetic data set we use parameter vectors $\boldsymbol{\beta}_{1,1} = (2,3,0,0)$,  $\boldsymbol{\beta}_{1,2} = \boldsymbol{\beta}_{2,1} = (1,0,0,1)$, and $\boldsymbol{\beta}_{2,2} = (2,0,2,0)$.  See Appendix for details on simulating from the model.  In Figure \ref{fig:syncounts} we illustrate the simulated data and show the loglikelihood during the first iterations of MCMC [after being initialized with $\beta \sim N(\beta_{true},.5^2)$].

@@

\begin{itemize}
\item Classroom:  Perhaps within a couple of the classrooms we can infer subgroups who tend to obey different relational event dynamics.
\item Email: In small organizations there may be groups of people who tend to have a similar style of interaction, and who also share a pattern of interaction with those outside the group or in another group.
\item Citation networks: Perhaps some groups of papers obey some types of rich-get-richer effects more than others.
\item Other
\end{itemize}

@@

>>>>

Statistical methods for analyzing network data have become increasingly useful for studying  phenomenon ranging from people communicating online to protein interactions \cite{Goldenberg2009}. One class of statistical models for network data uses latent variables to help model unobserved heterogeneity.  For example, the stochastic blockmodel \cite{Nowicki2001, Kemp} assumes each node in the network belongs to some block (or cluster) and parametrizes the probability of edges between nodes of each block.  % Such approaches are especially useful for large-scale network data where higher-order dependencies can cause models such as exponential random graph models to be too complex to fit.

Network data, however, is often collected as a sequence of events occurring over time.   Recently several works have adapted models from event history analysis \cite{} to provide continuous time models of network-based event data \cite{Butts2008,Brandes2009,Perry2011,Stadtfeld2010,Stadtfeld2011,Opsahl2011,Vu2011,Vu2011a}.  These models allow one to specify how the process depends on the previous history of events.  In this way one may incorporate theories about the underlying processes and make predictions about future data conditioned on the past.

The above continuous time network models have two major drawbacks: 1) the entire network is assumed to have identical dynamics, and 2) the occurrence of any event can affect the rate at which any other event occurs.  Both aspects may be unrealistic.  Consider email communication in a small organization comprised of several teams.  Each team may have a different pattern for collaborating via email, and in many cases emails between one pair of individuals will not affect emailing behavior between a separate pair of individuals.

Borrowing from the intuition of stochastic blockmodels, we propose a hierarchical model of continuous time network data that learns latent clusters of nodes which share similar patterns of interaction.  [TODO: Explain how our experiments show that this helps.]   [TODO: perhaps use ``role'' terminology.]

@@

%Each interaction then has a set of periods $d \in D_{ij}$ each with a start time $a_d$, an end time $b_d$, and a rate $\lambda_d$.
Consider a nonhomogeneous Poisson process with  intensity $\lambda(t)$ that is piecewise constant with respect to a set of knots $\tau$.  We can then write the likelihood of $M$ events as
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda(t_m) \exp\left\{ - \int_{0}^{t_M} \lambda(s)ds \right\} \\
&= \prod_{m=1}^M \lambda(t_m) \prod_{k=1}^{|\tau|} \exp\left\{ - (\tau_{k} - \tau_{k-1}) \lambda(\tau_k) \right\}
\end{align}
\noindent where the $m$th event occurs at time $t_m$, the intensity function $\lambda(t)$ is left continuous, and each $\tau_k \in [0,t_M]$.
% \begin{align}
% \mathcal{L}(A|\theta) &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}}  \exp\left\{ - \int_{0}^{t_M} \lambda_{i}(\tau | \cdot)d\tau \right\} \\
% &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}} \prod_{v \in D_{i}} \exp\left\{ - (b_v - a_v) \lambda_{i}(b_v | \cdot ) \right\}
% \end{align}

One can extend the above to marked point processes where each event contains additional information.  In the context of relational events occurring among $N$ nodes, for example, we let the \emph{risk set} $\mathcal{R}$ of possible events include all allowed dyads.  Let each dyad $(i,j) \in \mathcal{R}$ have an intensity function $\lambda_{ij}(t)$ that is piecewise constant.  Assume each node belongs to a cluster $z_i$. Let $\tau_{i,j,m}$ be the time  of the changepoint for $\lambda_{i,j}$ prior to the $m$th event and let $\mathcal{R}_{i,j}$ be the set of dyads involving either $i$ or $j$. \footnote{We further assume 1) all intensity functions change at times $t=0$ and $t=t_M$, and 2) the first event is drawn uniformly from the risk set.}

\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}_{i_m,j_m}}\exp\{ - (t_m - \tau_{i,j,m}) \lambda_{ij}(t_m | z_i,z_j) \}
\end{align}

@@

For a given dyad $(i,j)$ and time $t$ we may also have a vector of statistics $\mathbf{s}(t,i,j|\mathcal{A}_t,\mathbf{z})$ that is a function of the previous event history  $\mathcal{A}_t = \{(t_m,i_m,j_m): t_m \in [0,t)\}$  and the latent cluster assignments $\mathbf{z}$.   As shown in Figure \ref{fig:example}, we assume each intensity function $\lambda_{ij}(t)$ may only change following an event involving either $i$ or $j$.  Note the statistics $\mathbf{s}(t,i,j)$ also do not change until an event involving either $i$ or $j$ occurs.  We model the intensity functions via a log linear model
\begin{align}
\log \lambda_{ij}(t | \mathcal{A}_t,\mathbf{z}) = \boldsymbol{\beta}_{z_i,z_j} \mathbf{s}(t,i,j|\mathcal{A}_t,\mathbf{z}).
\end{align}
where for each pair of clusters $(z_i,z_j)$ we have a vector of parameters $\boldsymbol{\beta}_{z_i,z_j}$ that corresponds to the covariate vector $\mathbf{s}_{ij}(t|\cdot)$.

@@

We construct $\mathbf{s}(t,i,j)$ using a similar set of statistics as used in \cite{Butts2008,Vu2011}. Let $v_{ijm} \in [0,M]$ be the index of the last event where $(i,j)$ occurred (n.b. $t_{v_{ijm}} = \tau_{ijm}$). If $(i,j)$ has never occurred, we set $v_{ijm}=0$.  
\begin{enumerate}
\item Dyad count: $s_{1}(t,i,j) = \sum_{m:t_m<t} I(i_m=i) / m$
\item Sender out-degree: $s_{1}(t,i,j) = \sum_{m:t_m<t} I(i_m=i) / m$
\item Sender in-degree: $s_{2}(t,i,j) = \sum_{m:t_m<t} I(j_m=i) / m$
\item Receiver out-degree: $s_{3}(t,i,j) = \sum_{m:t_m<t} I(i_m=j)/m$
\item Receiver in-degree: $s_{4}(t,i,j) = \sum_{m:t_m<t} I(j_m=j)/m$
\item Reciprocity (AB-BA): $s_{5}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-taking (AB-BY): $s_{6}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-usurping (AB-XA): $s_{7}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-usurping (AB-XB): $s_{8}(t,i,j) = I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
\item Turn-continuing (AB-AY): $s_{9}(t,i,j) =  I(i_m=i,j_m=j,i_{v_{ijm}}=j,j_{v_{ijm}}=i)$
%\item Number of shared two-paths: $s_{10}(t,i,j) =   \sum_{m:t_m<t} \sum_{r=1}^NI(i_m=i,j_m=r or i_m=r,j_m=j)$
% \item Shared contacts (since last occurrence): $s_{ij10}(t,i,j) = \sum_{r=1}^N I(i_m=i,j_m=j,i_{v_{ijm}}=i,j_{v_{ijm}}=r)$
% \item Triadic closure (since last occurrence): $s_{ij11}(t,i,j) = \sum_{r=1}^N I(i_m=i,j_m=j,i_{v_{ijm}}=r,j_{v_{ijm}}=j)$
% \item Shared contacts (since last occurrence): $s_{ij12}(t,i,j) = \sum_{r=1}^N I(i_m=i,j_m=j,i_{v_{ijm}}=r,j_{v_{ijm}}=r)$
\end{enumerate}

@@

\subsection{Relation to other models}

This is reminiscent of the stochastic blockmodel \cite{Nowicki2001,Kemp} which models the probability of a dyad as $p(y_{ij}) =\mbox{logit}^{-1}( \eta_{z_i,z_j})$ where $\eta_{z_i,z_j}$ is essentially a mixing rate between group $z_i$ and group $z_j$.  Here, however, the blockmodel structure facilitates the study of intra-group and inter-group dynamics via a continuous-time network model.

The above framework generalizes several important special cases.  The first is one where events within each block share the rate at which they occur.  This can be implemented by only having an intercept statistic, $s_0(t,i,j) = 1$.  As these intensities do not change under this specification, the likelihood simplifies to 
$$\mathcal{L}(\mathcal{A}|\beta) = \prod_{m=1}^M \lambda_{i_m,j_m} \prod_{(i,j) \in \mathcal{R}} \exp\{-t_M \lambda_{i,j}\}$$
where $ \lambda_{ij} = \exp\{\boldsymbol{\beta}_{z_i,z_j}\}$.  Analogous to the stochastic block model for static networks, this model posits each dyad is a homogeneous Poisson process and all dyads within block $(z_i,z_j)$ have the intensity $\exp\{\boldsymbol{\beta}_{z_i,z_j}\}$.

@@

% \subsection{Approximate likelihood methods}

% TODO: Discuss how one might sample the likelihood.  Cite Raftery paper.

% TODO: Look at performance of this with respect to bias and performance measure

@@

We check our model fitting procedure using a small synthetic data set involving 10 nodes from 2 clusters where 1) the first cluster has an increased tendency for reciprocity, 2) members of the second cluster have an increased tendency to continue speaking, and 3) interactions between groups are more likely to be repeated.  The specification of $\textbf{s}$ is therefore $s(t,i,j) = [s_0, s_{5}(t,i,j), s_{9}(t,i,j), s_{11}(t,i,j)]$.  For the synthetic data set we use parameter vectors $\boldsymbol{\beta}_{1,1} = (2,3,0,0)$,  $\boldsymbol{\beta}_{1,2} = \boldsymbol{\beta}_{2,1} = (1,0,0,1)$, and $\boldsymbol{\beta}_{2,2} = (2,0,2,0)$.  See Appendix for details on simulating from the model.  In Figure \ref{fig:syncounts} we illustrate the simulated data and show the loglikelihood during the first iterations of MCMC [after being initialized with $\beta \sim N(\beta_{true},.5^2)$].

@@

\begin{itemize}
%\item Classroom:  Perhaps within a couple of the classrooms we can infer subgroups who tend to obey different relational event dynamics.
\item Email: In small organizations there may be groups of people who tend to have a similar style of interaction, and who also share a pattern of interaction with those outside the group or in another group.
%\item Citation networks: Perhaps some groups of papers obey some types of rich-get-richer effects more than others.
\item We collected tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 that contained the hashtag \texttt{#rstats}.  This hashtag is used to denote messages pertaining to the R statistical computing environment and sometimes statistical discussion more generally.  We collect dyadic events by selecting tweets beginning with the \texttt{@} symbol (called a \emph{mention}), and mark the first mentioned user as the recipient.  Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.  We use the subset of 487 users who participated in more than one event.
\end{itemize}

@@

\section{Conclusion}
 We propose a hierarchical approach for modeling event-based network data that is analogous to recent hierarchical extensions for latent position models \cite{Handcock2007} and exponential random graph models \cite{Schweinberger2011}.  The method combines a latent variable framework (stochastic blockmodels) with a local dependence model for event sequences (relational event models) to provide detailed models of event dynamics among subsets of nodes while simultaneously allowing for heterogeneity in dynamics of the network as a whole.
